Extracting data for time slice analyses

### 2017-12-18 analyses/01-extract-data-for-analyses.Rmd
Order slugs so it  matches later analyses and remove bears
Minor tidying of code
Corrected age bug in Brusatte and Bapst

## The latest version of Claddis (on development on my own branch)
install_github("TGuillerme/Claddis")
library(Claddis)

@@

```{r}
## Loading the matrix
## Not needed if running all the code at once
## matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))

@@

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
## matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

@@

# Tidy the tree and the data
tree <- makeNodeLabel(tree, method = "number", prefix = "n")
tree$root.time <- max(tree.age(tree)[, 1])
cleaned_data <- clean.data(matrix$matrix, tree)
matrix$matrix <- cleaned_data$data
tree <- cleaned_data$tree

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
## matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

Heath et al bears
-----------

```{r}
slug <- "bears"

# Tidy the tree and the data
tree <- makeNodeLabel(tree, method = "number", prefix = "n")
tree$root.time <- max(tree.age(tree)[, 1])
cleaned_data <- clean.data(matrix$matrix, tree)
matrix$matrix <- cleaned_data$data
tree <- cleaned_data$tree

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
## matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

# Tidy the tree and the data
tree <- makeNodeLabel(tree, method = "number", prefix = "n")
tree$root.time <- max(tree.age(tree)[, 1])
cleaned_data <- clean.data(matrix$matrix, tree)
matrix$matrix <- cleaned_data$data
tree <- cleaned_data$tree

## Remove

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
## matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

>>>>

## The Thomas' Claddis development version
## (contains faster AncStateEstMatrix and MorphDistMatrixFast functions)
install_github("TGuillerme/Claddis")
library(Claddis)

@@

```{r}
## Loading the matrix
## Not needed if running all the code at once
matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))

@@

## Loading the FADLAD
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)

## Remove the taxa not present in the tree but in the FADLAD
absent_in_tree <- clean.data(FADLAD, tree)$dropped_rows
if(!any(is.na(absent_in_tree))) {
    FADLAD <- FADLAD[-match(absent_in_tree, rownames(FADLAD)),]
}

## Getting the tree ages
tree_ages <- tree.age(tree)

## Scaling with the latest FADLAD
tree$root.time <- max(tree_ages[,1] + min(FADLAD[,2]))

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
# matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
#                                  uncertainty.threshold = 0.95)
# saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Loading the FADLAD
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)

## Remove the taxa not present in the tree but in the FADLAD
absent_in_tree <- clean.data(FADLAD, tree)$dropped_rows
if(!any(is.na(absent_in_tree))) {
    FADLAD <- FADLAD[-match(absent_in_tree, rownames(FADLAD)),]
}

## Getting the tree ages
tree_ages <- tree.age(tree)

## Scaling with the latest FADLAD
tree$root.time <- max(tree_ages[,1] + min(FADLAD[,2]))

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
# matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
#                                   uncertainty.threshold = 0.95)
# saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
# matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
#                                   uncertainty.threshold = 0.95)
# saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

@@
